MAESTROeX: A Massively Parallel Low Mach Number Astrophysical Solver

### 2019-03-19 MAESTROeX_I/results.tex
note about scaling

\subsection{Scaling}
Scaling with OpenMP

>>>>

\subsection{Scaling}
In Figure XXX we show weak scaling results for a spherical, full-star sub-chandrasekhar mass white dwarf calculation.
The x-axis represents total core count (in this case, the total number of OpenMP threads), and the y-axis is the wallclock time per time step.
These simulations were performed using the NERSC cori system on the Intel Xeon Phi (KNL) partition.
We split each KNL node to contain 4 MPI processes with 16 threads each.
The computational domain for each simulation is divided into $64^3$ grid cells, and we assign 1 MPI process to each grid.
We used simulations ranging from $256^3$ grid cells (64 MPI processes, corresponding to 1024 total threads) up to $1536^3$ grid cells (13,824 MPI processes, corresponding to 221,184 total threads).
Note that the largest simulation used roughly 36\% of the entire computational system.
We see that the total increas in wallclock time from the smallest to largest simulation is roughly 41\%, which is quite remarkable given that there are 3 linear solves per time step.
\MarginPar{Making new plots splitting out projections vs. everything else.}
